Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-12-07 Manuscript.Rmd
Trying to not be stupid and creating a thresholding function for FV. But it's not working

  nVertices <- 59412
  tempVec <- rep(-1, nVertices)
  temp <- grep(MOI, colnames(Data))
  tempVec[Data$Vertex] <- Data[[temp]]
  write.table(file = paste(SubjID,"_",MOI,'_dataforCifti.txt', sep=""), tempVec, row.names = F, col.names = F, dec = ".")

@@

### *Pattern stability over time*

@@

``` {r Partition comparison: all 2 (Fig. 4), fig.align="center", out.width = "40%", fig.cap = "Figure 4. Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately. PCC is well aligned across individuals, while mPFC shows clear topographical heterogeneity.", echo=FALSE, message = FALSE, cache = TRUE}
par(xpd=T)
corrplot(RI_PCC,
         is.corr = F, 
         method = "color",
         type = "lower", 
         tl.pos = "n", 
         tl.cex = 0.1, 
         cl.lim = c(0,1),
         cl.length = 3,
         addgrid.col = "grey99",
         cl.pos = "r",
         mar = c(1,1,2,0))
corrplot(RI_PFC, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.cex = 0.1,
         cl.pos = "n",
         addgrid.col = "grey90",
         mar = c(1,1,2,0), 
         add = T)
segments(0.5,0.5,0.5,100.5, lwd = 2)
segments(0.5,0.5,100.5,0.5, lwd = 2)
segments(0.5,100.5,100.5,100.5, lwd = 2)
segments(100.5,0.5,100.5,100.5, lwd = 2)
mtext(expression(bold("Subject Partitions")), line = 3)
mtext(expression(bold("Subject Partitions")), side = 2, line = -0.8)
mtext(expression(bold("mPFC")), line = 2, at = par("usr")[1]+0.73*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 4, at = par("usr")[1]+0.18*diff(par("usr")[1:2]), col = "steelblue4")

@@

``` {r Partition comparison: halves (Fig. 5), fig.align="center", out.width = "60%", fig.cap = "Figure 5. Similarity matrices for 10 example participants showing pattern agreement across days for the whole partition (left), and for PCC and mPFC separately (right). These figures show high agreement within (but not between) subjects, with mPFC again showing significant variability.", echo=FALSE, message = FALSE, cache = TRUE}
# plots
par(mfrow=c(1,2))
corrplot(RI_all_between_halves_plot, 
         is.corr = F, 
         method = "color",
         addgrid.col = "grey90",
         tl.pos = "n", 
         tl.col = "black",
         tl.cex = 0.1,
         cl.pos = "n",
         cl.lim = c(0,1),
         cl.length = 3,
         mar = c(1.1,1.1,1.1,1.1))
# segments(0.5,0.5,0.5,20.5, lwd = 2)
# segments(0.5,0.5,20.5,0.5, lwd = 2)
# segments(0.5,20.5,20.5,20.5, lwd = 2)
# segments(20.5,0.5,20.5,20.5, lwd = 2)
mtext(expression(bold("Subjects (Day 1 and Day 2)")), line = 1)
mtext(expression(bold("Subjects (Day 1 and Day 2)")), side = 2, line = 3)
corrplot(RI_PCC_halves_plot, 
         is.corr = F,     
         method = "color",
         type = "lower", 
         tl.pos = "n", 
         cl.lim = c(0,1),
         cl.pos = "r",
         addgrid.col = "grey90",
         cl.length = 3)
corrplot(RI_PFC_halves_plot, 
         is.corr = F, 
         method = "color",
         type = "upper", 
         tl.pos = "n", 
         cl.pos = "n", 
         addgrid.col = "grey90",
         add = T)
mtext(expression(bold("Subjects (Day 1 and Day 2)")), line = 1)
mtext(expression(bold("mPFC")), line = -0.15, at = par("usr")[1]+0.8*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 0.6, at = par("usr")[1]+0.09*diff(par("usr")[1:2]), col = "steelblue4")
```

@@

``` {r Partition comparison: session similarity matrices (Fig. 7), fig.align="center", out.width = "60%", fig.cap = "Figure 7. Similarity matrices showing pattern agreement across sessions for the whole partition (left), and for PCC and mPFC separately (right) (10 example subjects). The pattern from the daily analysis is preserved, with marked individuality for mPFC, but not PCC.", echo=FALSE, message = FALSE, cache = TRUE}
# plot
par(mfrow=c(1,2))
corrplot(RI_all_between_sess_plot, 
         is.corr = F, 
         method = "color", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         cl.lim = c(-0.03,1),
         cl.pos = "n",
         cl.length = 3,
         mar = c(1.1,1.1,1.1,1.1), 
         addgrid.col = "grey90")
# segments(0.5,0.5,0.5,40.5, lwd = 2)
# segments(0.5,0.5,40.5,0.5, lwd = 2)
# segments(0.5,40.5,40.5,40.5, lwd = 2)
# segments(40.5,0.5,40.5,40.5, lwd = 2)
mtext(expression(bold("Subjects (Session)")), line = 1)
mtext(expression(bold("Subjects (Session)")), side = 2, line = 3)
corrplot(RI_PCC_sess_plot, 
         is.corr = F, 
         method = "color", 
         type = "lower", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         cl.lim = c(0,1),
         cl.length = 3,
         cl.pos = "r", 
         addgrid.col = "grey90")
# segments(0.5,0.5,0.5,20.5, lwd = 2)
# segments(0.5,0.5,20.5,0.5, lwd = 2)
# segments(0.5,20.5,20.5,20.5, lwd = 2)
# segments(20.5,0.5,20.5,20.5, lwd = 2)
corrplot(RI_PFC_sess_plot, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.col = "black", 
         cl.pos = "n", 
         addgrid.col = "grey90",
         add = T)
mtext(expression(bold("Subjects (Session)")), line = 1)
mtext(expression(bold("mPFC")), line = 0, at = par("usr")[1]+0.8*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 1, at = par("usr")[1]+0.09*diff(par("usr")[1:2]), col = "steelblue4")
```

>>>>

  nVertices <- 59412
  tempVec <- rep(0, nVertices)
  temp <- grep(MOI, colnames(Data))
  tempVec[Data$Vertex] <- Data[[temp]]
  write.table(file = paste(SubjID,"_",MOI,'_dataforCifti.txt', sep=""), tempVec, row.names = F, col.names = F, dec = ".")

@@

### *Thresholding*
``` {r Threshold this stupid stuff}
# This function will select a two-tailed fiedler vector threshold with respect to the stability of the vertex
# The threshold will be based on proportion DMN given by thresholdRange
threshFV <- function(Data, thresholdRange = c(0.01, 0.99), nthresh = 50) {

  ## Check if the proportions even go that low, otherwise replace by next most stable low/high value
  # get the 2 values with highest reports (this should be stable upper/lower proportions)
  stableExtremes <- sort(table(Data$slidePropDMN), decreasing = T)[seq(2)]
  stableExtremes <- sort(as.numeric(names(stableExtremes)))

  # if the values are not extreme enough, replace the original threshold with the new stable ones
  if (thresholdRange[1] < stableExtremes[1]) {

    thresholdRange[1] <- stableExtremes[1]

  if (thresholdRange[2] > stableExtremes[2]) {

    thresholdRange[2] <- stableExtremes[2]

  ## Run the actual process
  # placeholder to be returned
  thresholds <- c(NA,NA)

  # start the counter at chance
  meanProp <- 0.5

  # select a range of FV values
  thresh <- seq(0, min(Data$FiedlerVec), length.out = nthresh)

  # Iterate over the possible FV until DMN affiliations go below 1%
  count <- 1
  while (meanProp > thresholdRange[1]) {

    # get the mean proportion of DMN from remaining vertices based on putative threshold
    meanProp <- Data %>% filter(FiedlerVec <= thresh[count]) %>% summarize(mean(slidePropDMN))

    # if a threshold meets requirement, store its value
    if (meanProp <= thresholdRange[1]) {
      thresholds[1] <- thresh[count]
    }
    print(count)
    print(meanProp)
    print(thresh[count])
    count <- count + 1

  # repeat for the upper threshold
  # restart parameters
  meanProp <- 0.5
  thresh <- seq(0, max(abs(Data$FiedlerVec)), length.out = nthresh)

  # Iterate over the possible FV until DMN affiliations go over 99%
  count <- 1
  while (meanProp < thresholdRange[2]) {

    # get the mean proportion of DMN from remaining vertices based on putative threshold
    meanProp <- Data %>% filter(FiedlerVec > thresh[count]) %>% summarize(mean(slidePropDMN))

    # if a threshold meets requirement, store its value
    if (meanProp >= thresholdRange[2]) {
      thresholds[2] <- thresh[count]
    }

    count <- count + 1

  return(round(thresholds, digits = 5))

}
```
### *Pattern stability over time*

@@

``` {r Partition comparison: all 2 (Fig. 4), fig.align="center", out.width = "40%", fig.cap = "Figure 4. Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately. PCC is well aligned across individuals, while mPFC shows clear topographical heterogeneity.", echo=FALSE, message = FALSE, cache = TRUE}
par(xpd=T)
corrplot(RI_PCC,
         is.corr = F, 
         method = "color",
         type = "lower", 
         tl.pos = "n", 
         tl.cex = 0.1, 
         #cl.lim = c(0,1),
         cl.length = 3,
         addgrid.col = "grey99",
         cl.pos = "r",
         mar = c(1,1,2,0))
corrplot(RI_PFC, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.cex = 0.1,
         cl.pos = "n",
         addgrid.col = "grey90",
         mar = c(1,1,2,0), 
         add = T)
segments(0.5,0.5,0.5,100.5, lwd = 2)
segments(0.5,0.5,100.5,0.5, lwd = 2)
segments(0.5,100.5,100.5,100.5, lwd = 2)
segments(100.5,0.5,100.5,100.5, lwd = 2)
mtext(expression(bold("Subject Partitions")), line = 3)
mtext(expression(bold("Subject Partitions")), side = 2, line = -0.8)
mtext(expression(bold("mPFC")), line = 2, at = par("usr")[1]+0.73*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 4, at = par("usr")[1]+0.18*diff(par("usr")[1:2]), col = "steelblue4")

@@

``` {r Partition comparison: halves (Fig. 5), fig.align="center", out.width = "60%", fig.cap = "Figure 5. Similarity matrices for 10 example participants showing pattern agreement across days for the whole partition (left), and for PCC and mPFC separately (right). These figures show high agreement within (but not between) subjects, with mPFC again showing significant variability.", echo=FALSE, message = FALSE, cache = TRUE}
# plots
par(mfrow=c(1,2))
corrplot(RI_all_between_halves_plot, 
         is.corr = F, 
         method = "color",
         addgrid.col = "grey90",
         tl.pos = "n", 
         tl.col = "black",
         tl.cex = 0.1,
         cl.pos = "n",
         #cl.lim = c(0,1),
         cl.length = 3,
         mar = c(1.1,1.1,1.1,1.1))
# segments(0.5,0.5,0.5,20.5, lwd = 2)
# segments(0.5,0.5,20.5,0.5, lwd = 2)
# segments(0.5,20.5,20.5,20.5, lwd = 2)
# segments(20.5,0.5,20.5,20.5, lwd = 2)
mtext(expression(bold("Subjects (Day 1 and Day 2)")), line = 1)
mtext(expression(bold("Subjects (Day 1 and Day 2)")), side = 2, line = 3)
corrplot(RI_PCC_halves_plot, 
         is.corr = F,     
         method = "color",
         type = "lower", 
         tl.pos = "n", 
         #cl.lim = c(0,1),
         cl.pos = "r",
         addgrid.col = "grey90",
         cl.length = 3)
corrplot(RI_PFC_halves_plot, 
         is.corr = F, 
         method = "color",
         type = "upper", 
         tl.pos = "n", 
         cl.pos = "n", 
         addgrid.col = "grey90",
         add = T)
mtext(expression(bold("Subjects (Day 1 and Day 2)")), line = 1)
mtext(expression(bold("mPFC")), line = -0.15, at = par("usr")[1]+0.8*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 0.6, at = par("usr")[1]+0.09*diff(par("usr")[1:2]), col = "steelblue4")
```

@@

``` {r Partition comparison: session similarity matrices (Fig. 7), fig.align="center", out.width = "60%", fig.cap = "Figure 7. Similarity matrices showing pattern agreement across sessions for the whole partition (left), and for PCC and mPFC separately (right) (10 example subjects). The pattern from the daily analysis is preserved, with marked individuality for mPFC, but not PCC.", echo=FALSE, message = FALSE, cache = TRUE}
# plot
par(mfrow=c(1,2))
corrplot(RI_all_between_sess_plot, 
         is.corr = F, 
         method = "color", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         cl.lim = c(-0.03,1),
         cl.pos = "n",
         cl.length = 3,
         mar = c(1.1,1.1,1.1,1.1), 
         addgrid.col = "grey90")
# segments(0.5,0.5,0.5,40.5, lwd = 2)
# segments(0.5,0.5,40.5,0.5, lwd = 2)
# segments(0.5,40.5,40.5,40.5, lwd = 2)
# segments(40.5,0.5,40.5,40.5, lwd = 2)
mtext(expression(bold("Subjects (Session)")), line = 1)
mtext(expression(bold("Subjects (Session)")), side = 2, line = 3)
corrplot(RI_PCC_sess_plot, 
         is.corr = F, 
         method = "color", 
         type = "lower", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         #cl.lim = c(0,1),
         cl.length = 3,
         cl.pos = "r", 
         addgrid.col = "grey90")
# segments(0.5,0.5,0.5,20.5, lwd = 2)
# segments(0.5,0.5,20.5,0.5, lwd = 2)
# segments(0.5,20.5,20.5,20.5, lwd = 2)
# segments(20.5,0.5,20.5,20.5, lwd = 2)
corrplot(RI_PFC_sess_plot, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.col = "black", 
         cl.pos = "n", 
         addgrid.col = "grey90",
         add = T)
mtext(expression(bold("Subjects (Session)")), line = 1)
mtext(expression(bold("mPFC")), line = 0, at = par("usr")[1]+0.8*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 1, at = par("usr")[1]+0.09*diff(par("usr")[1:2]), col = "steelblue4")
```
